### 2018-05-19 Sections/optical_routers.tex
Minor crossbar

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multi_channel_multi_port_switch}
\caption{A completely general multi-channel multi-port switch may be constructed using a staggered grid of two-port switches (grey boxes), shown here for \mbox{$n=6$} ports. This allows the implementation of an arbitrary permutation between input and output ports, enabling all $n$ channels to be simultaneously utilised and routed across distinct input-to-output routes. This requires \mbox{$\left\lceil \frac{n^2}{2}\right\rceil - n + 1$} two-port switches in total.} \label{fig:multi_channel_multi_port_switch} \index{Multi-channel multi-port switches}	
\end{figure}

@@

A general multi-port switching architecture, that gained popularity in the early days of channel-switched telecommunications networks\index{Channel-switched network}, is the crossbar architecture, whereby $n$ inputs are mapped to $n$ outputs via a binary permutation matrix, which controls a lattice of \mbox{$2\times 2$} switches. The general layout of the architecture is shown in Fig.~\ref{fig:crossbar_switch}, and an example of a routing sequence corresponding to a particular binary control matrix is shown in Fig.~\ref{fig:crossbar_example}. Clearly the scheme requires $n^2$ two-port switches to implement arbitrary \mbox{$n\times n$} mode permutations. The main disadvantage of this scheme is that different paths within a given permutation experience differing optical depth, ranging from 1 to \mbox{$2n-1$}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{crossbar_switch}
\caption{Crossbar architecture for multi-port switching. Each orange box represents a \mbox{$2\times 2$} switch, of any physical implementation.} \label{fig:crossbar_switch}	
\end{figure}

@@

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{multi_channel_multi_port_switch}
\caption{A completely general multi-channel multi-port switch may be constructed using a staggered grid of two-port switches (grey boxes), shown here for \mbox{$n=6$} ports. This allows the implementation of an arbitrary permutation between input and output ports, enabling all $n$ channels to be simultaneously utilised and routed across distinct input-to-output routes. This requires \mbox{$\left\lceil \frac{n^2}{2}\right\rceil - n + 1$} two-port switches in total. Optical depth is approximately equal across all input-to-output paths.} \label{fig:multi_channel_multi_port_switch} \index{Multi-channel multi-port switches}	
\end{figure}

@@

A general multi-port switching architecture, that gained popularity in the early days of channel-switched telecommunications networks\index{Channel-switched network}, is the crossbar architecture, whereby $n$ inputs are mapped to $n$ outputs via a binary permutation matrix, which controls a lattice of \mbox{$2\times 2$} switches. The general layout of the architecture is shown in Fig.~\ref{fig:crossbar_switch}, and an example of a routing sequence corresponding to a particular binary control matrix is shown in Fig.~\ref{fig:crossbar_example}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{crossbar_switch}
\caption{Crossbar architecture for multi-port switching. Each orange box represents a \mbox{$2\times 2$} switch, of any physical implementation. The switching sequence of the constituent two-port switches is defined by a binary \mbox{$n\times n$} permutation matrix, whose elements determine whether a given two-port switch flips modes or doesn't.} \label{fig:crossbar_switch}	
\end{figure}

@@

Clearly the scheme requires $n^2$ two-port switches to implement arbitrary \mbox{$n\times n$} mode permutations. The main disadvantage of this scheme is that in general different paths within a given permutation experience differing optical depths, ranging from 1 (best case) to \mbox{$2n-1$} (worst case).
